\section{Project Activity}
During this project a number of deadlines must be met, four in total. To meet these deadlines \textbf{Alset Innovations} has compiled a list of activities which must be met to complete the \textbf{PROJE4} course.

\subsection{Deadlines}
The first deadline for the \textbf{PROJE4} course is the completion of the Plan of Approach this must be completed and delivered on the 18th of February 23:59. After this \textbf{Alset Innovations} will be dedicated to completing assessment 1 and 2. For which the main focus will be on designing the code for the \textbf{STM32} as this is required for the first assessment. The secondary focus will be on designing a schematic for the motor driver which will be used to order parts and for assessment 2 to design a \textbf{PCB}. These assessments must be completed in week 7 and week 12 respectively.

The final assessment will be held in the 19th week of the project, for this assessment a presentation and a demonstration must be held. In addition to this a written report must also be delivered.

\subsection{Activities}
To meet these deadlines the following activities will be completed by \textbf{Alset Innovations}

\begin{itemize}
    \item Complete planning to complete the Plan of Approach.
    \item Complete the Plan of Approach.
    \item Design a circuit to read the HAL sensors.
    \item Design code to read the HAL sensors.
    \item Design code to control the timing of the \textbf{MOSFETS} using the HAL sensor data.
    \item Design code to create a PWM signal to control the motor RPM using an input as reference.
    \item Design code to create an interface using \textbf{I2C} or \textbf{UART} to display data on a touch-display connected to a \textbf{Raspberry pi model 3B}. Or design code to display data on a \textbf{SSD1306 I2C OLED} display and to connect a psychical interface using buttons and potentiometer.
    \item Design a schematic with the most important components to drive the motor and order these parts.
    \item Based on testing of the schematic add necessary components, protective circuitry and additional filters to the schematic.
    \item Test the function of the updated schematic and continue to improve and test the schematic until the schematic functions as is required.
    \item After completing the schematic the PCB can be designed.
    \item Complete the PCB with the required parts and connect the motor and interface to complete the \textbf{PROJE4} course.
\end{itemize}

In addition to these activities a set of deliverables must be completed to successfully complete the assessments these deliverables will be explained in chapter seven Product.

