\section{Project Boundaries}
The \textbf{PROJE4} course is set to go on for 20 weeks, in these 20 weeks \textbf{Alset Innovations} is tasked with designing a motor driver for a 78W motor. To complete this task the project de designer has create a set of requirement which must be met.

\begin{itemize}
    \item The motor controller must be able to continuously turn a 24 V, 78 W
    BLDC motor in a closed loop configuration using hall sensor feedback.
    \item  The design must use one of the following two micro-controllers in order to
    generate the motor control signals.
    \begin{itemize}
        \item RP2040 
        \item STM32F103C8T6 
    \end{itemize}
    \item The hall sensor signals must be processed in the micro-controller. It
    is not permitted to use an advanced motor driver IC which handles the
    hall-signals internally.
    \item Discrete transistors must be used to control the three phases of the motor. Any additional components such as gate drivers can be implemented using integrated circuits.
    \item The final product must be on a custom PCB that has been designed and assembled by the student group themselves. 
    \item The controller must measure the current delivered to the motor and be able to send it to the user interface. 
    \item The user interface must provide a control input (throttle) that allows the speed of the motor to be controlled, and must also be able to display the measured speed (rpm) and current.
\end{itemize}

These requirements are the minimum requirements necessary to complete the \textbf{PROJE4} course with a passing grade. In order to excel \textbf{Alset Innovations} must improve the design according to their own ideas. This can be anything in the theme of this project as long as it stays within the budget.

In summary \textbf{Alset Innovations} will have to design a motor driver schematic and PCB, an user interface to control the motor driver and to excell must come up with their own ideas to improve the design.